### 2022-03-24 Analysis/01-EffectCorrelationStats.Rmd
Updated functions and results for new nomenclature

```{r, warning = FALSE}
## Pooling the data per scenarios
scenario_RF_norm <- multi.pool(whole_data, param = c("maxi", "mini", "rand"),
                               metric = "RF", best = "norm")
scenario_Tr_norm <- multi.pool(whole_data, param = c("maxi", "mini", "rand"),
                               metric = "Tr", best = "norm")

>>>>

```{r, warning = FALSE}
## Pooling the data per scenarios
scenario_RF_norm <- multi.pool(whole_data, param = c("mini", "maxi", "rand"),
                               metric = "RF", best = "norm")
scenario_Tr_norm <- multi.pool(whole_data, param = c("mini", "maxi", "rand"),
                               metric = "Tr", best = "norm")

### 2022-03-24 Analysis/02-EffectCorrelationFullResults.Rmd
Updated functions and results for new nomenclature

```{r, warning = FALSE}
## Pooling the data per scenarios
scenario_RF_norm <- multi.pool(whole_data, param = c("maxi", "mini", "rand"),
                               metric = "RF", best = "norm")
scenario_Tr_norm <- multi.pool(whole_data, param = c("maxi", "mini", "rand"),
                               metric = "Tr", best = "norm")
scenario_RF_null <- multi.pool(whole_data, param = c("maxi", "mini", "norm"),
                               metric = "RF", best = "rand")
scenario_Tr_null <- multi.pool(whole_data, param = c("maxi", "mini", "norm"),
                               metric = "Tr", best = "rand")

>>>>

```{r, warning = FALSE}
## Pooling the data per scenarios
scenario_RF_norm <- multi.pool(whole_data, param = c("mini", "maxi", "rand"),
                               metric = "RF", best = "norm")
scenario_Tr_norm <- multi.pool(whole_data, param = c("mini", "maxi", "rand"),
                               metric = "Tr", best = "norm")
scenario_RF_null <- multi.pool(whole_data, param = c("mini", "maxi", "norm"),
                               metric = "RF", best = "rand")
scenario_Tr_null <- multi.pool(whole_data, param = c("mini", "maxi", "norm"),
                               metric = "Tr", best = "rand")

### 2022-03-24 Writing/Palaeontology/draft.tex
Updated functions and results for new nomenclature

\begin{figure}[!htbp]
\centering
   \includegraphics[width=0.9\textwidth]{outline.eps}
\caption{Outline of the simulation protocol: the first step includes both the simulation and the modification of the matrices (thin solid lines); the second step includes tree inference using maximum parsimony and Bayesian inference methods (thick solid lines); the third step includes comparing the resulting tree topologies (dashed lines). $n$ and $m$ corresponds to the number of characters with a character difference $<0.25$ and $>0.75$ respectively.}
\label{Fig:outline}
\end{figure}

\subsection{Simulating discrete morphological matrices}

@@

\subsection{Comparing topologies}
We compared the topologies using the same approach as in \cite{Guillerme2016146}: we measured both the Robinson-Foulds distance \citep{RF1981} and the triplets distance \citep{dobson1975triplets} between the trees inferred from the ``maximised'', ``minimised'' and ``randomised'' matrices and the tree inferred from the ``normal'' matrix.
We explored the effect of character difference on recovering the ``normal'' topology by comparing the ``maximised'', ``minimised'' and ``randomised'' trees to the ``normal'' tree (Figs \ref{Fig:RF_results_best} and \ref{Fig:Tr_results_best} and supplementary materials 3 Figs 10 and 11).
Note that we are not comparing the trees to the ``true'' tree used to simulate the matrices.
First, in biology, this tree is always unknown.
Second, our objective is to measure the direct effect of character correlation approximated by the difference in topology between the ``normal'', ``maximised'' and ``minimised'' trees.

@@

\begin{figure}[!htbp]
\centering
   \includegraphics[width=1\textwidth]{RF_results_best.eps}
\caption{\small{Effect of character difference on recovering the ``normal'' topology in terms of clade conservation ($NTS_{RF}$). The y axis represents the Normalised Tree Similarity using Robinson-Fould distance for matrices with 25, 75 and 150 f from top to bottom respectively. The x axis represents the different character difference scenarios and tree inference method with the ``maximised'' character difference in Bayesian (red) and under maximum parsimony (orange), the ``minimised'' character difference in Bayesian (dark green) and under maximum parsimony (light green) and the ``randomised'' character difference in Bayesian (dark blue) and under maximum parsimony (light blue) for matrices of 100, 350 and 1000 characters in the panels from left to right.}}
\label{Fig:RF_results_best}
\end{figure}

>>>>

\begin{figure}[!htbp]
\centering
   \includegraphics[width=0.9\textwidth]{outline.eps}
\caption{Outline of the simulation protocol: the first step includes both the simulation and the modification of the matrices (thin solid lines); the second step includes tree inference using maximum parsimony and Bayesian inference methods (thick solid lines); the third step includes comparing the resulting tree topologies (dashed lines). $n$ and $m$ corresponds to the number of characters with a character difference $<0.25$ and $>0.75$ respectively.}
\label{Fig:outline}
\end{figure}
''
\subsection{Simulating discrete morphological matrices}

@@

\subsection{Comparing topologies}
We compared the topologies using the same approach as in \cite{Guillerme2016146}: we measured both the Robinson-Foulds distance (\textcolor{blue}{the differences in clade compositions}, \citealt{RF1981}) and the triplets distance (\textcolor{blue}{the differences in tips positions}; \citealt{dobson1975triplets}) between the trees inferred from the maximised correlation, minimised correlation and randomised matrices and the tree inferred from the unperturbed matrix (Figs \ref{Fig:RF_results_best} and \ref{Fig:Tr_results_best} and supplementary materials 3 Figs 10 and 11).
Note that we are not comparing the trees to the starting tree used to simulate the matrices.
This is because, first, in biology, this tree is always unknown; and second, our objective is to measure the direct effect of character correlation approximated by the difference in topology between the unperturbed,  maximised correlation and minimised correlation trees.

@@

\begin{figure}[!htbp]
\centering
   \includegraphics[width=1\textwidth]{RF_results_best.eps}
\caption{\small{Effect of character difference on recovering the topology from the unperturbed matrix in terms of clade conservation ($NTS_{RF}$). The y axis represents the Normalised Tree Similarity using Robinson-Fould distance for matrices with 25, 75 and 150 taxa from top to bottom respectively. The x axis represents the different character difference scenarios and tree inference method with the ``maximised'' character difference in Bayesian (red) and under maximum parsimony (orange), the ``minimised'' character difference in Bayesian (dark green) and under maximum parsimony (light green) and the ``randomised'' character difference in Bayesian (dark blue) and under maximum parsimony (light blue) for matrices of 100, 350 and 1000 characters in the panels from left to right.}}
\label{Fig:RF_results_best}
\end{figure}

### 2022-03-24 Writing/Tables/Tab_pooledscharacters_test.tex
Updated results
bold main results
Updated functions and results for new nomenclature

% latex table generated in R 3.4.4 by xtable 1.8-2 package
% Tue Mar 27 14:03:13 2018
\begin{table}[ht]
\centering
\begin{tabular}{llr|rl}
  \hline
metric & test & bhatt.coeff & statistic & p.value \\ 
  \hline
RF & c100:c350 & \textbf{0.99} & 190357.500 & 1 \\ 
   & c100:c1000 & \textbf{0.98} & 174085.500 & \textbf{0.001} \\ 
   & c350:c1000 & \textbf{0.984} & 180460.000 & \textbf{0.032} \\ 
  Tr & c100:c350 & \textbf{0.961} & 166609.500 & \textbf{0} \\ 
   & c100:c1000 & \textbf{0.956} & 151389.500 & \textbf{0} \\ 
   & c350:c1000 & \textbf{0.981} & 178793.500 & \textbf{0.014} \\ 
   \hline
\end{tabular}
\caption{Difference between the pooled number of characters. Bhatt.coeff is the Bhattacharrya Coefficient (probability of overlap), the statistic and the p.value are from a non-parametric wilcoxon test (with Bonferonni-Holm correciton)} 
\label{Tab_pooledscharacters_test}
\end{table}

>>>>

% latex table generated in R 4.1.3 by xtable 1.8-4 package
% Thu Mar 24 14:24:05 2022
\begin{table}[ht]
\centering
\begin{tabular}{llr|rr}
  \hline
metric & test & bhatt.coeff & statistic & p.value \\ 
  \hline
RF & c100 vs. c350 & 0.965 & 48263.500 & 0.000 \\ 
   & c100 vs. c1000 & 0.914 & 37714.500 & 0.000 \\ 
   & c350 vs. c1000 & 0.976 & 53138.000 & 0.000 \\ 
  Tr & c100 vs. c350 & 0.929 & 40253.000 & 0.000 \\ 
   & c100 vs. c1000 & 0.826 & 27923.000 & 0.000 \\ 
   & c350 vs. c1000 & 0.957 & 48164.500 & 0.000 \\ 
   \hline
\end{tabular}
\caption{Differences between the Normalised Tree Similarities in terms of clade conservation (Robinson-Foulds distances - RF) and taxa displacement (Triplets - Tr) for the three different number of characters: 100 (c100), 350 (c350) and 1000 (c1000). Bhatt.coeff is the Bhattacharrya Coefficient (probability of overlap), the statistic and the p.value are from a non-parametric Wilcoxon test (with Bonferonni-Holm correction).} 
\label{Tab_pooledscharacters_test}
\end{table}
